---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# monomgcv

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/gzt/monomgcv/branch/master/graph/badge.svg)](https://codecov.io/gh/gzt/monomgcv?branch=master)
[![R build status](https://github.com/gzt/monomgcv/workflows/R-CMD-check/badge.svg)](https://github.com/gzt/monomgcv/actions)
<!-- badges: end -->

Turning somebody's gist for a monotonic GAM into a package (experimental).

Based on https://gist.github.com/willtownes/f598e5c2344043675566603d29b6c2d6

I make no representations about this package, use at your own risk.

## Installation

You can install the released version of monomgcv from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("monomgcv")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("gzt/monomgcv")
```
## Example

This is a basic example which shows you how to fit a monotonic GAM with two different 
settings for knots based on the existing example code in `mgcv`.

```{r example}
library(monomgcv)
 x <- runif(100) * 4 - 1
 x <- sort(x)
 f <- exp(4 * x) / (1 + exp(4 * x))
 y <- f + rnorm(100) * 0.1
 plot(x, y)
 fv <- mspline(x, y, 5)
 lines(x, predict(fv, x), col = "red")
 fv <- mspline(x, y, 10)
 lines(x, predict(fv, x), col = "blue")
 legend("bottomright", lty = 1, paste0("k=", c(5, 10)),
        col = c("red", "blue"))
```

  ## Code of Conduct
  
  Please note that the monomgcv project is released with a 
  [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). 
  By contributing to this project, you agree to abide by its terms.
